Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-10-02 vertical-thermal-review_SI.Rmd
small edit in SI

Through the above process, 202 articles were saved for careful evaluation. To this, articles shared by co-authors and references mentioned in other studies collectively added 32 studies.

@@

In total, following careful review, we identified **70** articles as relevant and included their results in Tables 1-2.

>>>>

Through the above process, 202 articles were saved for careful evaluation. To this, additional studies were 
shared by co-authors.

@@

In total, following careful review, we identified **75** articles as relevant and included their results in Tables 1-2.
